Congestion Control Aware Queuing

### 2019-10-17 tex/paper.tex
Removed anonymity

We evaluate our \gls{qdisc} using the \ifx\removeHeaders\tempYes{}\texttt{py-virtnet}\else{}[removed for anonymity]\fi{} toolkit to build a virtual network using Linux's network namespaces. We initialize the buffer size for our \gls{qdisc} to 100 packets per flow like in fq.

>>>>

We evaluate our \gls{qdisc} using the \texttt{py-virtnet} (\url{https://github.com/CN-TU/py-virtnet}) toolkit to build a virtual network using Linux's network namespaces. We initialize the buffer size for our \gls{qdisc} to 100 packets per flow like in fq.
